Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
Add more acknowledgements

    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

\section{Experiments}
\label{sec:experiments}
We experimentally evaluated our approach   
on the well-benchmarked Aurora-4 \citep{parihar2002aurora} noisy speech recognition task. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which were added to the clean data. Every clean and noisy
utterance has been 
% what kind of frequency characteristics?
filtered to simulate the phone quality recording using P.341 \citep{parihar2002aurora}. The training
data contains 4400 clean utterances and 446 utterances for each noise condition,
i.e., a total of 2676 noisy utterances.
The test set consists of clean data, data corrupted by 6 noise types, and data 
recorded with a different microphone for both the clean and noisy conditions.

@@

% TODO
% dima: we need to emphasize that the unseen noises are very important
To evaluate the impact of our method on generalization to \emph{unseen} noises (the
most typical situation in practice),
we performed 6 experiments with different sets of noises seen during training.
The networks were trained
on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
restaurant, street, and train. The last training group included all noises and therefore matched the
standard multi-condition training setup. For every training group, we trained the
baseline and the invariance model, where we branched out at the $4^{th}$ layer to a
binary classifier predicting clean versus noisy data. Due to the imbalance between amounts of clean and
noisy utterances, we had to oversample noisy frames to ensure that every mini-batch contained
equal number of clean and noisy speech frames.

@@

We would like to thank Yaroslav Ganin, David Warde-Farley for insightful discussions,
developers of Theano~\citep{theano2016theano}, Blocks, and Fuel~\citep{MerrienboerBDSW15} 
for great toolkits.

>>>>

    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-shaped structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network ($D$) and 
    a target classifier network ($R$). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

\section{Experiments}
\label{sec:experiments}
We experimentally evaluated our approach   
on the well-benchmarked Aurora-4 \citep{parihar2002aurora} noisy speech recognition task. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which were added to the clean data. Every clean and noisy
utterance has been 
% TODO!!!!
% what kind of frequency characteristics?
filtered to simulate the phone quality recording using P.341 \citep{parihar2002aurora}. The training
data contains 4400 clean utterances and 446 utterances for each noise condition,
i.e., a total of 2676 noisy utterances.
The test set consists of clean data, data corrupted by 6 noise types, and data 
recorded with a different microphone for both the clean and noisy conditions.

@@

To evaluate the impact of our method on generalization to \emph{unseen} noises (the
most typical situation in practice),
we performed 6 experiments with different sets of noises seen during training.
The networks were trained
on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
restaurant, street, and train. The last training group included all noises and therefore matched the
standard multi-condition training setup. For every training group, we trained the
baseline and the invariance model, where we branched out at the $4^{th}$ layer to a
binary classifier predicting clean versus noisy data. Due to the imbalance between amounts of clean and
noisy utterances, we had to oversample noisy frames to ensure that every mini-batch contained
equal number of clean and noisy speech frames.

@@

We would like to thank Yaroslav Ganin, David Warde-Farley for insightful discussions,
developers of Theano~\citep{theano2016theano}, Blocks, and Fuel~\citep{MerrienboerBDSW15} 
for great toolkits. 
The authors would like to acknowledge the support of the following agencies for
research funding and computing support: NSERC, Calcul Qu\'{e}bec, Compute Canada,
the Canada Research Chairs and CIFAR. Dmitriy Serdyuk thanks Samsung for partial
financial support of this work.
